Lower tax brackets and employment levels, and people living in populous areas are more likely to vote for Biden

### 2024-12-16 paper/paper.qmd
last changes

The estimand is the effect of income level, employment status, and living area on the odds of voting for Biden, measured as the change in predicted odds associated with each predictor, holding other factors constant.

@@

The appendix explores survey methodologies, focusing on sampling and observational data in the CCES dataset. It compares methodologies, examines sampling variability and bias, and uses simulations to expand on points in the data section.

This analysis was conducted in R, using tidyverse for data manipulation, dataverse for dataset access, knitr for report generation, modelsummary for model interpretation, and rstanarm for Bayesian regression [@citeR; @Dataverse; @Knitr; @Modelsummary; @Rstanarm; @Tidybayes; @Dplyr]. Visualizations were created with ggplot, and portions of the discussion and appendix were assisted by ChatGPT4 [@chatgpt].

>>>>

The estimand is the probability that a voter supports Joe Biden as opposed to Donald Trump, conditional on the socio-economic factors of living environment, employment status, and income levels.

@@

The appendix explores survey methodologies, focusing on sampling and observational data in the CCES dataset. It compares methodologies and discusses sampling variability and biases.

This analysis was conducted in R, using tidyverse for data manipulation, dataverse for dataset access, knitr for report generation, modelsummary for model interpretation, and rstanarm for Bayesian regression [@citeR; @Dataverse; @Knitr; @Modelsummary; @Rstanarm; @Tidybayes; @Dplyr]. Visualizations were created with ggplot, and portions of the discussion and appendix were assisted by ChatGPT4 [@chatgpt].
\newpage
